Timeliness of security updates for Android

### 2014-11-12 securityupdates.tex
Add some more text to the caption of figure 1

\begin{figure}[h]
\centering
\includegraphics[width=\columnwidth]{figures/proportioninsecure}
\caption{Proportion of devices running insecure, maybe insecure and secure versions of Android against time}
\label{fig:proportioninsecure}
\end{figure}

>>>>

\begin{figure}[h]
\centering
\includegraphics[width=\columnwidth]{figures/proportioninsecure}
\caption{Proportion of devices running insecure, maybe insecure and secure versions of Android against time.
The red vertical lines are caused by vulnerabilities being discovered.
This graph is explained further in XXX.}
\label{fig:proportioninsecure}
\end{figure}
